\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

% Define colors
\definecolor{techblue}{RGB}{0, 102, 204}
\definecolor{techgray}{RGB}{240, 240, 240}

% Set title format
\titleformat{\section}{\large\bfseries\color{techblue}}{}{0em}{}[\titlerule]

% Set hyperlink color
\hypersetup{
    colorlinks=true,
    linkcolor=techblue,
    urlcolor=techblue,
}

% Custom commands for contact info
\newcommand{\contact}[2]{\textbf{#1:} \texttt{#2}\\}

\begin{document}

\begin{center}
    \Huge \textbf{Your Name} \\
    \vspace{0.2cm}
    \large Your Job Title \\
    \vspace{0.5cm}
    \faEnvelope \ \href{mailto:your.email@example.com}{your.email@example.com} \\
    \faLinkedin \ \href{https://www.linkedin.com/in/yourprofile}{linkedin.com/in/yourprofile} \\
    \faGithub \ \href{https://github.com/yourusername}{github.com/yourusername} \\
\end{center}

\vspace{1cm}

\section*{Summary}
A brief summary about yourself, your skills, and your career objectives. Highlight your passion for technology and innovation.

\section*{Education}
\begin{itemize}[leftmargin=*]
    \item \textbf{Your Degree}, Your Major \\
    Your University, Year of Graduation
    \item \textbf{Additional Certifications} \\
    Certification Name, Issuing Organization, Year
\end{itemize}

\section*{Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Job Title} \\
    Company Name, Location \\
    \textit{Month Year -- Present} \\
    Responsibilities and achievements in this role.
    
    \item \textbf{Previous Job Title} \\
    Previous Company Name, Location \\
    \textit{Month Year -- Month Year} \\
    Responsibilities and achievements in this role.
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item Programming Languages: Python, JavaScript, etc.
    \item Frameworks: React, Node.js, etc.
    \item Tools: Git, Docker, etc.
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{Project Name} \\
    Brief description of the project, technologies used, and your contributions.
    
    \item \textbf{Another Project Name} \\
    Brief description of the project, technologies used, and your contributions.
\end{itemize}

\section*{Publications}
\begin{itemize}[leftmargin=*]
    \item \textbf{Title of Your Article} \\
    Brief description of the article and where it was published.
\end{itemize}

\section*{Interests}
A brief list of your interests related to technology, innovation, and any other relevant hobbies.

\end{document}